### 2021-11-03 publication/inference.tex
Fix citet
dimensionality reduction

Having completed the definition of the FFBM, we wish to leverage it 
to perform inference. Given a vertex-labelled graph $(A, X)$,
the goal is to sample from the posterior distribution
of $\theta$:
%
\begin{equation}
	\label{eqn:theta-target}
	\theta \sim p(\theta | A, X).
\end{equation}
%
We propose an iterative approach to obtain samples
$\theta^{(t)}$ from $p(\theta|A,X)$. We first draw samples $b^{(t)}$ 
from the block membership posterior distribution,
and then use each $b^{(t)}$ to obtain a corresponding
sample $\theta^{(t)}$:
%
\begin{align}
	b^{(t)} &\sim p ( b | A, X )  \label{eqn:b-samples},\\
	\theta^{(t)} &\sim p\left(\theta | X, b^{(t)} \right). \label{eqn:theta-samples}
\end{align}
%
Both of these sampling steps can be implemented through a
Markov chain Monte-Carlo approach via a Metropolis-Hastings 
algorithm \cite{hastings-alg}, as a two-level Markov chain.
The resulting samples 
for $\theta^{(t)}$ are unbiased in the sense that the expectation of 
their distribution is the target posterior distribution:
%
\begin{equation}
\Expect_{b^{(t)}} \left[p \left( \theta | X, b^{(t)} \right) \right] = \sum_{b \in [B]^N} p(\theta | X, b) p(b | A, X) = p(\theta | A, X).
\label{eqn:theta-unbiased}
\end{equation}
%
This is an example of a pseudo-marginal approach. Indeed, \citet{pseudo-marginal} show that~(\ref{eqn:theta-unbiased})
% the unbiased result in equation 
is sufficient to prove that, for large enough $t$, $\theta^{(t)} \sim p(\theta | A, X)$, as required.

@@

Once the samples $\left\{ \theta^{(t)} \right\} \sim p(\theta | A, X)$
have been obtained, we can compute the empirical mean and standard deviation of each component of $\theta$. Switching back to matrix notation, we define $\theta = W$, such that $W_{ij}$ is the weight component for block $i$ and feature $j$. We can then define:
%
\begin{equation}
	\hat{\mu}_{ij} \coloneqq \frac{1}{|\Tcal_\theta|} \sum_{t \in \Tcal_\theta} W_{ij}^{(t)} \qquad \textrm{and} \qquad
	\hat{\sigma}_{ij}^2 \coloneqq \frac{1}{|\Tcal_\theta|} \sum_{t \in \Tcal_\theta} \left( W_{ij}^{(t)} - \hat{\mu}_{ij} \right)^2.
\end{equation}
%
A simple heuristic to discard the least important features requires specifying a cutoff $c > 0$ and a multiplier $k > 0$. We define the function $\Fcal_i(j)$ 
as in~(\ref{eqn:fij}) and only keep features with indices $d \in \Dcal'$, where $\Dcal'$ is given in~(\ref{eqn:kept-feature-set}).
%
\begin{align}
	\Fcal_i(j) &\coloneqq (\hat{\mu}_{ij} - k \hat{\sigma}_{ij}, \hat{\mu}_{ij} + k \hat{\sigma}_{ij}) \cap (-c, +c),
	\label{eqn:fij} \\
	\Dcal' &\coloneqq \left\{ j \in [D] : \exists i \in [B] \textrm{ s.t. }  \Fcal_i(j) = \emptyset \right\}
	\label{eqn:kept-feature-set}
\end{align}
%
Intuitively, this means discarding any feature $j$ for which 
$(\hat{\mu}_{ij} - k\hat{\sigma}_{ij}, \hat{\mu}_{ij} + k \hat{\sigma}_{ij})$ overlaps with
$(-c, c)$ for all block indices $i$. If we were to use the Laplace approximation for the posterior $p(W_{ij} | A, X) \approx \Gaussian(W_{ij}; \hat{\mu}_{ij}, \hat{\sigma}_{ij}^2)$, then this is analogous to a hypothesis test on the value of $W_{ij}$ as in~(\ref{eqn:hyp-test-discard});
then $\Dcal'$ comprises all features $j$ for which $H_1$ is accepted at least once for some $i \in [B]$.
%
\begin{equation}
	H_0: |W_{ij}| \leq c \qquad
	H_1: |W_{ij}| > c
	\label{eqn:hyp-test-discard}
\end{equation}
%
The multiplier $k$ in~(\ref{eqn:fij}) determines the degree of significance of the result. However, as the Laplace approximation is not exact, we regard this as a useful heuristic and not an exact method. Conversely, we could fix $k=k_0$ and the dimension of our reduced feature set $|\Dcal'|=D'$. We would then like to find the largest value of $c$ such that $|\Dcal'|=D'$ given $k=k_0$:
%
\begin{equation}
	c^* = \argmax \{c>0\; : \;|\Dcal'| = D', k=k_0\}.
	\label{eqn:c-star}
\end{equation}
%
This has the advantage of fixing the number of reduced dimensions.

>>>>

Having completed the definition of the FFBM, we wish to leverage it 
to perform inference. Given a vertex-labelled graph $(A, X)$,
the goal is to sample from the posterior distribution
of $\theta$:
%
\begin{equation}
	\label{eqn:theta-target}
	\theta \sim p(\theta | A, X).
\end{equation}
%
We propose an iterative approach to obtain samples
$\theta^{(t)}$ from $p(\theta|A,X)$. We first draw samples $b^{(t)}$ 
from the block membership posterior distribution,
and then use each $b^{(t)}$ to obtain a corresponding
sample $\theta^{(t)}$:
%
\begin{align}
	b^{(t)} &\sim p ( b | A, X )  \label{eqn:b-samples},\\
	\theta^{(t)} &\sim p\left(\theta | X, b^{(t)} \right). \label{eqn:theta-samples}
\end{align}
%
Both of these sampling steps can be implemented through a
Markov chain Monte-Carlo approach via a Metropolis-Hastings 
algorithm \cite{hastings-alg}, as a two-level Markov chain.
The resulting samples 
for $\theta^{(t)}$ are unbiased in the sense that the expectation of 
their distribution is the target posterior distribution:
%
\begin{equation}
\Expect_{b^{(t)}} \left[p \left( \theta | X, b^{(t)} \right) \right] = \sum_{b \in [B]^N} p(\theta | X, b) p(b | A, X) = p(\theta | A, X).
\label{eqn:theta-unbiased}
\end{equation}
%
This is an example of a pseudo-marginal approach. Indeed, Andrieu and Roberts \cite{pseudo-marginal} show that~(\ref{eqn:theta-unbiased})
% the unbiased result in equation 
is sufficient to prove that, for large enough $t$, $\theta^{(t)} \sim p(\theta | A, X)$, as required.

@@

Once the samples $\left\{ \theta^{(t)} \right\} \sim p(\theta | A, X)$
have been obtained, we can compute the empirical mean and standard deviation of each component of $\theta = \{ w_i \}_{i=1}^{B}$:
%
\begin{equation}
	\hat{\mu}_{ij} \coloneqq \frac{1}{|\Tcal_\theta|} \sum_{t \in \Tcal_\theta} w_{ij}^{(t)} \qquad \textrm{and} \qquad
	\hat{\sigma}_{ij}^2 \coloneqq \frac{1}{|\Tcal_\theta|} \sum_{t \in \Tcal_\theta} \left( w_{ij}^{(t)} - \hat{\mu}_{ij} \right)^2.
\end{equation}
%
A simple heuristic to discard the least important features requires specifying a cutoff $c > 0$ and a multiplier $k > 0$. We define the function $\Fcal_i(j)$ 
as in~(\ref{eqn:fij}) and only keep features with indices $d \in \Dcal'$, where $\Dcal'$ is given in~(\ref{eqn:kept-feature-set}).
%
\begin{align}
	\Fcal_i(j) &\coloneqq (\hat{\mu}_{ij} - k \hat{\sigma}_{ij}, \hat{\mu}_{ij} + k \hat{\sigma}_{ij}) \cap (-c, +c),
	\label{eqn:fij} \\
	\Dcal' &\coloneqq \left\{ j \in [D] : \exists i \in [B] \textrm{ s.t. }  \Fcal_i(j) = \emptyset \right\}
	\label{eqn:kept-feature-set}
\end{align}
%
Intuitively, this means discarding any feature $j$ for which 
$(\hat{\mu}_{ij} - k\hat{\sigma}_{ij}, \hat{\mu}_{ij} + k \hat{\sigma}_{ij})$ overlaps with
$(-c, c)$ for all block indices $i$. If we were to use the Laplace approximation for the posterior $p(w_{ij} | A, X) \approx \Gaussian(w_{ij}; \hat{\mu}_{ij}, \hat{\sigma}_{ij}^2)$, then this would be analogous to a hypothesis test on the magnitude of $w_{ij}$ compared to $c$ with multiplier $k$ in~(\ref{eqn:fij}) determines the degree of significance of the result. However, as the Laplace approximation is not exact, we regard this as a useful heuristic and not an exact method. Conversely, if we want to fix the number of dimensions in our reduced feature set $|\Dcal'|=D'$, the problem then becomes finding the largest value of $c$ such that $|\Dcal'|=D'$ given $k=k_0$:
%
\begin{equation}
	c^* = \argmax \{c>0\; : \;|\Dcal'| = D', k=k_0\}.
	\label{eqn:c-star}
\end{equation}
